### 2016-11-29 dissertation/prelim_basis.tex
dissertation v2:minor amendment

\chapter{Gr\"ober Basis and Algebraic Geometry} \label{ch:ideals}
This chapter reviews fundamental concepts of commutative and 
computer algebra which are used in this work. 
Specifically, this chapter covers monomial ordering, polynomial ideals and 
varieties, and the computation of \Grobner bases.
It also overviews elimination theory as well as Hilbert's Nullstellensatz 
theorems and how
they apply to Galois fields. The results of these theorems are used in polynomial
abstraction and formal verification of Galois field circuits and 
are discussed 
in subsequent chapters. The material of this chapter is
mostly referred from the textbooks \cite{ideals:book} \cite{gb_book} and 
previous work by {\it Lv} \cite{lv:phd} as well as {\it Pruss} \cite{pruss:tcad15}.

@@

The high computational complexity if Gr\"obner basis computation is treated as an issue
because of its high cost on time and space. Concretely, for arbitrary polynomial set, 
the worst case computation time/space cost of its Gr\"obner basis is doubly exponential bounded -- $q^{q^{O(|\phi|)}}$
\cite{dube1986complexity}. However, in practice such as applications of circuit verification, 
the polynomial is well restricted rather than arbitrary.
Gao et al. \cite{gao:qe-gf-gb} proves that when the number of variables and degree of polynomials 
are restricted, the complexity reduces to single exponential $q^O(|\phi|)$.
This provides the possibility to make use of Gr\"obner basis under restricted situations,
which is the theoretic basis of this dissertation.

@@

When we compute the reduced \Grobner basis, $G_r$, of \{$J + J_0$\} with 
respect to this ordering, $G_r$ = \{$g_1, \dots, g_{14}\}:$
\begin{align*}
g_1: B^4+B; 
~~g_2: b_0+b_1 \alpha + B; 
~~g_3: a_0+a_1 \alpha + A;  \nonumber \\
~~g_4: c_0+c_1 \alpha + c_2 \alpha + c_3(\alpha+1)+Z;
g_5: r_0+c_1+c_2; 
~~g_6: z_0+c_0+c_3; \nonumber \\
~~g_7: z_1+r_0+c_3; 
~~{\bf g_8: Z+A\cdot B};
~~g_9: b_1+B^2+B; 
~~g_{10}: a_1+A^2+A; \nonumber \\
~~g_{11}: c_3+a_1\cdot b_1
g_{12}: c_2+a_1\cdot b_1 \alpha + a_1 \cdot B; 
~~g_{13}: c_1+a_1\cdot b_1 \alpha +b_1 A; 
~~g_{14}: A^4+A  \nonumber
\end{align*}

>>>>

\chapter{Gr\"ober Basis and Algebraic Geometry} \label{ch:ideals}
This chapter reviews fundamental concepts of commutative and 
computer algebra which are used in this work. 
Specifically, this chapter covers monomial ordering, polynomial ideals and 
varieties, and the computation of \Grobner bases.
It also overviews elimination theory as well as Hilbert's Nullstellensatz 
theorems and how
they apply to Galois fields. The results of these theorems are used in polynomial
abstraction and formal verification of Galois field circuits and 
are discussed 
in subsequent chapters. The material of this chapter is
mostly referred from the textbooks \cite{ideals:book,gb_book} and 
previous work by {\it Lv} \cite{lv:phd} as well as {\it Pruss} \cite{pruss:tcad15}.

@@

The high computational complexity if Gr\"obner basis computation is treated as an issue
because of its high cost on time and space. Concretely, for arbitrary polynomial set, 
the worst case computation time/space cost of its Gr\"obner basis is doubly exponential bounded -- $q^{q^{O(|\phi|)}}$
\cite{dube1986complexity}. However, in practice such as applications of circuit verification, 
the polynomial is well restricted rather than arbitrary.
Gao et al. \cite{gao:qe-gf-gb} proves that when the number of variables and degree of polynomials 
are restricted, the complexity reduces to single exponential $q^{O(|\phi|)}$.
This provides the possibility to make use of Gr\"obner basis under restricted situations,
which is the theoretic basis of this dissertation.

@@

When we compute the reduced \Grobner basis, $G_r$, of \{$J + J_0$\} with 
respect to this ordering, $G_r$ = \{$g_1, \dots, g_{14}\}:$
\begin{align*}
&g_1: B^4+B; 
~~g_2: b_0+b_1 \alpha + B; 
~~g_3: a_0+a_1 \alpha + A;  \nonumber \\
&g_4: c_0+c_1 \alpha + c_2 \alpha + c_3(\alpha+1)+Z;
g_5: r_0+c_1+c_2; 
~~g_6: z_0+c_0+c_3; \nonumber \\
&g_7: z_1+r_0+c_3; 
~~{\bf g_8: Z+A\cdot B};
~~g_9: b_1+B^2+B; 
~~g_{10}: a_1+A^2+A; \nonumber \\
&g_{11}: c_3+a_1\cdot b_1
g_{12}: c_2+a_1\cdot b_1 \alpha + a_1 \cdot B; 
~~g_{13}: c_1+a_1\cdot b_1 \alpha +b_1 A; 
~~g_{14}: A^4+A  \nonumber
\end{align*}
